Appendix for "NGO Repression as a Predictor of Worsening Human Rights Abuses

### 2021-11-17 manuscript/appendix.Rmd
Build appendix with targets

---
title: "NGO Repression as a Predictor of Worsening Human Rights Abuses"
short-title: "NGO Repression and Human Rights"
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  email: schaudhry@lclark.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
date: "July 20, 2021"
published: Under review
code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/canary-ngos/>"
abstract: >-
  An increasing number of countries have recently cracked down on non-governmental organizations (NGOs). Much of this crackdown is sanctioned by law and represents a bureaucratic form of repression that could indicate more severe human rights abuses in the future. This is especially the case for democracies, which unlike autocracies, may not aggressively attack civic space. We explore if crackdowns on NGOs predict broader human rights repression. Anti-NGO laws are among the most subtle means of repression and attract lesser domestic and international condemnation compared to the use of violence. Using original data on NGO repression, we test whether NGO crackdown is a predictor of political terror, and violations of physical integrity rights and civil liberties. We find that while formal de jure laws provide little information in predicting future repression, their patterns of implementation, or de facto civil society repression, predicts worsening respect for physical integrity rights and civil liberties.
# keywords: civil society, NGOs, repression, human rights, political terror, civil liberties
word-count: "7,159"
thanks: >-
  We would like to thank participants of the 2021 International Studies Association (ISA) convention, and the "Human Rights on the Edge: The Future of International Human Rights Law and Practice" workshop hosted by the Global Human Rights Hub at Arizona State University for their comments and feedback.
reference-section-title: References
bibliography: bibliography.bib
toc: false
title-page: true
endnotes: true
endfloat: false
mainfont: Cochineal
sansfont: Inter
author-note: >-
  Suparna Chaudhry, PhD, Assistant Professor of International Affairs, Department of International Affairs, Lewis \& Clark College; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University. 
correspondence: >-
  Correspondence concerning this article should be addressed to Andrew Heiss, PhD, Department of Public Management and Policy, Andrew Young School of Policy Studies, Georgia State University, 14 Marietta Street NW, Suite 357, Atlanta, GA 30303. Contact: aheiss@gsu.edu
editor_options: 
  chunk_output_type: console
---

# Appendix

## Modeling approach

@@

### Equation for PTS models

@@

### R code for PTS models

@@

### Equation for latent human rights models

@@

### R code for latent human rights models

@@

## Improved cases

@@

## Complete model results

>>>>

---
title: 'Appendix for "NGO Repression as a Predictor of Worsening Human Rights Abuses"'
short-title: 'Appendix for "NGO Repression"'
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  email: schaudhry@lclark.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
date: "November 16, 2021"
# published: Under review
code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/canary-ngos/>"
reference-section-title: References
bibliography: bibliography.bib
toc: false
appendix: true
mainfont: Cochineal
sansfont: Inter
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# Figure out output format
is_docx <- knitr::pandoc_to("docx") | knitr::pandoc_to("odt")
is_latex <- knitr::pandoc_to("latex")
is_html <- knitr::pandoc_to("html")

# Word-specific things
table_format <- ifelse(is_docx, "huxtable", "kableExtra")  # Huxtable tables
conditional_dpi <- ifelse(is_docx, 300, 300)  # Higher DPI
conditional_align <- ifelse(is_docx, "default", "center")  # Word doesn't support align

# Knitr options
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  tidy.opts = list(width.cutoff = 120),  # Code width
  fig.retina = 3, dpi = conditional_dpi,
  fig.width = 7, fig.asp = 0.618,
  fig.align = conditional_align, out.width = "100%",
  fig.path = "output/figures/",
  cache.path = "output/_cache/",
  fig.process = function(x) {  # Remove "-1" from figure names
    x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
    if (file.rename(x, x2)) x2 else x
  }
)

# R options
options(
  width = 90,  # Output width
  dplyr.summarise.inform = FALSE,  # Turn off dplyr's summarize() auto messages
  knitr.kable.NA = "",  # Make NAs blank in kables
  kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
  modelsummary_factory_default = table_format,  # Set modelsummary backend
  modelsummary_format_numeric_latex = "plain"  # Don't use siunitx
)

# modelsummary regression table notes
if (is_latex) {
  model_note <- "Posterior means; 95\\\\% credible intervals in brackets" 
} else {
  model_note <- "Posterior means; 95% credible intervals in brackets"
}
```

```{r libraries-data, include=FALSE}
library(tidyverse)
library(targets)
library(kableExtra)
library(modelsummary)

withr::with_dir(here::here(), {
  source(tar_read(plot_funs))

  # Model tables
  tar_load(c(models_paper_pts, models_paper_lhr))

  # Load lookup list for coefficients in regression tables
  tar_load(coef_list)
})
```

# Modeling approach

@@

## PTS models

### Equation

@@

### R code

@@

## Latent human rights models

### Equation

@@

### R code

@@

# Improved cases

@@

# Complete model results
